Playing Games: A Case Study in Active Learning Applied to Game Theory

### 2015-07-22 paper/paper.tex
Setting up things to ease the creation of .docx
Giving up on wordifying.
Tidying up final version
- Fixing issue with full page (do not use \abstract{}...)
- Including acknowledgements to Zoe for help with Word
- link to twothirds library

\documentclass[12pt, a4paper]{article}

%\usepackage[backend=biber, firstinits=false , backref=false, url=true, isbn=true, style=draft]{biblatex}
\usepackage[backend=biber, firstinits=false , backref=false, url=true, isbn=true, style=numeric]{biblatex}
%\usepackage[backend=biber, firstinits=false , backref=false, url=true, isbn=true, style=authoryear]{biblatex}
\addbibresource{library.bib}

\usepackage{fullpage}

@@

\usepackage{wordlike}  % Make this look like word made it
%\usepackage{xcolor}
%\usepackage{sectsty}
%\sectionfont{\color{cyan}}
%\subsectionfont{\color{cyan}}

@@

@@

\abstract{
    This paper describes two active learning activities which aims to introduce
    students to the game theoretic concepts of best response dynamics and
    repeated game analysis.

@@

    The final section of this work describes how these activities fit in the
    pedagogic framework of a particular undergraduate mathematics class.
    Students generate data that can be used as context for the understanding of
    theoretic concepts. It is suggested that this framework is not restricted to
    the subject of game theory.
}

@@

@@

>>>>

\documentclass{article}

\usepackage{fullpage}
\usepackage{parskip}

@@

@@

\usepackage[backend=biber, firstinits=false , backref=false, url=true, isbn=true, style=numeric]{biblatex}
\addbibresource{library.bib}

@@

\begin{abstract}
    This paper describes two active learning activities which aims to introduce
    students to the game theoretic concepts of best response dynamics and
    repeated game analysis.

@@

    The final section of this work describes how these activities fit in the
    pedagogic framework of a particular undergraduate mathematics class.
    Students generate data that can be used as context for the understanding of
    theoretic concepts. It is suggested that this framework is not restricted to
    the subject of game theory.
\end{abstract}

@@

At the time of writing, software is being written to help quickly analyse plays of the game (and produce the graphs seen above). Documentation for this can be found here: \url{http://twothirds.readthedocs.org/}.

@@

\textbf{Acknowledgements}

The author would like to thank Dr Zo{\"e} Prytherch for her help with the typesetting of the published version of this manuscript.
